COG-ED Manuscript

### 2022-01-13 06_Paper/COG-ED/Manuscript.Rmd
added point to plot only for sign pipelines

@@

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
    geom_point() +
    geom_line() +
    theme_classic() +
    labs(x = NULL, y = "Fixed effects estimate") +
    scale_y_continuous(position = "right") +
    theme(axis.text.x = element_blank())

>>>>

  # add a column to plot only points that are significant

  sca_results$sign <- ifelse(sca_results$pvalue < .01, sca_results$beta, NA)

@@

  sca_upperplot <- ggplot(data = sca_results, aes(x = num, y = beta, color = predictor, group = predictor)) +
    geom_point(data = sca_results, aes(x = num, y = sign, color = predictor, group = predictor)) +
    geom_line() +
    theme_classic() +
    labs(x = NULL, y = NULL) +
    scale_y_continuous(position = "right") +
    ggtitle("Fixed effects estimate") +
    theme(axis.text.x = element_blank(), plot.title = element_text(hjust = 1))
